### 2018-01-18 Chapters/Chapter01.tex
Update on Overleaf.

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/bitcoin-H-increasing.png}
\caption{$\mathbf{E}[T]$ when H increases linearly with $u(t) = 1 + at$.\label{fig-bitcoin-H-increase}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-bitcoin-attack.png}
\caption{Probability of a successful attack according to the network's hash rate of the attacker ($\beta$).\label{fig-bitcoin-attack}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-tangle-example.pdf}
\caption{White nodes represent transactions that have been confirmed at least once. Green circles represent unconfirmed transactions (tips). Gray and dashed nodes are the transactions currently solving the proof-of-work in order to be propagated.\label{fig-tangle-example}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-tangle-swarm.pdf}
\caption{Suddenly the number of transactions per second increases and the width of the swarm grows. After a while, the number of transactions per second decreases and the width of the swarm shrinks.\label{fig-tangle-swarm}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-tangle-conflict.pdf}
\caption{The red nodes are transactions which had some conflict with previous transaction and were invalidated by the network. Notice that none of them have been confirmed.\label{fig-tangle-conflict}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-tangle-hist.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 15 minutes with new transactions rate changing between 1 and 15 tx/s.\label{fig-tangle-hist}}
\end{figure}

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{images/fig-tangle-hist-2.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 5 minutes with new transactions rate of 50 tx/s, i.e., very high load.\label{fig-tangle-hist-2}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/bitcoin-H-increasing.png}
\caption{$\mathbf{E}[T]$ when H increases linearly with $u(t) = 1 + at$.\label{fig-bitcoin-H-increase}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-bitcoin-attack.png}
\caption{Probability of a successful attack according to the network's hash rate of the attacker ($\beta$).\label{fig-bitcoin-attack}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-example.pdf}
\caption{White nodes represent transactions that have been confirmed at least once. Green circles represent unconfirmed transactions (tips). Gray and dashed nodes are the transactions currently solving the proof-of-work in order to be propagated.\label{fig-tangle-example}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-swarm.pdf}
\caption{Suddenly the number of transactions per second increases and the width of the swarm grows. After a while, the number of transactions per second decreases and the width of the swarm shrinks.\label{fig-tangle-swarm}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-conflict.pdf}
\caption{The red nodes are transactions which had some conflict with previous transaction and were invalidated by the network. Notice that none of them have been confirmed.\label{fig-tangle-conflict}}
\end{figure}

@@

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 15 minutes with new transactions rate changing between 1 and 15 tx/s.\label{fig-tangle-hist}}
\end{figure}

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist-2.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 5 minutes with new transactions rate of 50 tx/s, i.e., very high load.\label{fig-tangle-hist-2}}
\end{figure}
